### 2020-03-10 Common/chapters/paper_reproduction.tex
Julien and Johan: minors

First of all, when observing the loss plot, it is noticeable that the training and validation losses have the same behavior during the 50 epochs. This is a clear sign of good fit of the model on the data. All the features learned by the model on the training data are also applicable to the validation set. This situation is the optimal one. Regarding the slope of the curve, a big change occurs at epoch 17. This moment corresponds to the one where the learning rate is reduced by a factor of $100$ thanks to the \textit{reducelronplateau} function. In fact, at this moment, the validation AUC (the training is optimized according to this metric) was at its optimum with this learning rate. If this technique had not been used, the training loss would have continued to go down whereas the validation loss would have gone up immediately, which would have led to overfitting. Here, thanks to the learning rate scheduler, this scenario is avoided as the validation and training losses stay stable from this point onwards. The same behaviour is clearly noticeable for all other metrics.

Regarding the overall performance of the best model chosen at epoch 21, the latter generalizes well. This is particularly visible on the accuracy and AUC plots where the validation metrics are higher or equal to the training ones. The validation accuracy indicates that the model made the right class decision in approximately $75$\% of the time. Furthermore, as the model achieves a validation AUC of $0.76$, it shows that it has a good distinction capacity. In fact, the highest the AUC is, the highest is the ability of the model to predict benign lesions as benign and malignant lesions as malignant. Armato et al.~\cite{42} claim that a less-experienced radiologist can reach an AUC of $0.81$ and an expert an AUC of $0.91$. Consequently, this model is almost at the level of a radiologist, which is very promising. It is also important to keep in mind that the model was trained using only 164 patients (80\% of the 204 training patients), which suggests that even better results can be reached with more data.

@@

As the goal of the experiment was to reproduce the experiment of the paper, a comparison between the two models is necessary. The reproducted model achieved an AUC of $0.75$ on our test set (see Figure \ref{fig:paper_reproduction_auc_on_our_test_set}) using the authors' "enhanced prediction" technique, whereas the authors achieved an AUC $\in [0.876-0.994]$ with 95\% of confidence on their test set. Consequently, the model presented in this work has a slightly smaller AUC of $[0.126-0.244]$ than the one achieved in the paper. Multiple factors can explain this difference.

>>>>

First of all, when observing the loss plot, it is noticeable that the training and validation losses have the same behavior during the 50 epochs. This is a clear sign of good fit of the model on the data. All the features learned by the model on the training data are also applicable to the validation set. This situation is the optimal one. Regarding the slope of the curve, a big change occurs at epoch 17. This moment corresponds to the one where the learning rate is reduced by a factor of $100$ thanks to the \textit{reducelronplateau} function. In fact, at this moment, the validation AUC (the training is optimized according to this metric) is at its optimum with this learning rate. If this technique had not been used, the training loss would have continued to go down whereas the validation loss would have gone up immediately, which would have led to overfitting. Here, thanks to the learning rate scheduler, this scenario is avoided as the validation and training losses stay stable from this point onwards. The same behaviour is clearly noticeable for all other metrics.

Regarding the overall performance of the best model chosen at epoch 21, the latter generalizes well. This is particularly visible on the accuracy and AUC plots where the validation metrics are higher or equal to the training ones. The validation accuracy indicates that the model makes the right class decision in approximately $75$\% of the time. Furthermore, as the model achieves a validation AUC of $0.76$, it shows that it has a good distinction capacity. In fact, the highest the AUC is, the highest is the ability of the model to predict benign lesions as benign and malignant lesions as malignant. Armato et al.~\cite{42} claim that a less-experienced radiologist can reach an AUC of $0.81$ and an expert an AUC of $0.91$. Consequently, this model is almost at the level of a radiologist, which is very promising. It is also important to keep in mind that the model was trained using only 164 patients (80\% of the 204 training patients), which suggests that even better results can be reached with more data.

@@

As the goal of the experiment was to reproduce the experiment of the paper, a comparison between the two models is necessary. The reproduced model achieves an AUC of $0.75$ on our test set (see Figure \ref{fig:paper_reproduction_auc_on_our_test_set}) using the authors' "enhanced prediction" technique, whereas the authors achieved an AUC $\in [0.876-0.994]$ with 95\% of confidence on their test set. Consequently, the model presented in this work has a slightly smaller AUC of $[0.126-0.244]$ than the one achieved in the paper. Multiple factors can explain this difference.
